Age-related changes in plant growth and traits

### 2015-08-19 Accessory_figs.rmd
Rename *Inv variables

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
options(scipen=10)
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
words.bottom.right.logxy(mod)

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7.5}
par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
     xlim=c(1,700000),ylim=c(1,700000),xlab="Total reproductive investment (mg)",ylab="Investment in accessory tissues (mg)")
abline(0,1)
abline(-0.30103,1)
abline(-1,1)
text(120,350,"all RE to accessory tissues",srt=45)
text(12000,720,"10% RE to accessory tissues",srt=45)
text(5,1.5,"50%",srt=45)

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm(asin(sqrt(seedset))~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((ReproInv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
words.bottom.right.logy(mod)

mod <- lm(asin(sqrt(prop_propagule))~log(ReproInv),data=subset(SummaryInd,prop_propagule>0))
plot((ReproInv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
words.bottom.right.logy(mod)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(propagule_per_seed)~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((ReproInv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
words.bottom.right.logxy(mod)
```

@@

###5. What influences the correlation between RA and plant size (or total reproductive investment)?
  ***Don't trust anything until I know RA and ReproInv are correct, because PHPH and PUTU have huge influence on patterns***
```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30,warning=FALSE}
par(mfrow=c(5,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))

@@

- just looking among plants >3 years old  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2)) 
tmp <- SummaryInd %>%
  filter(ReproInv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_prepollen_all)

@@

tmp2 <- SummaryInd %>%
  filter(ReproInv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_packaging_dispersal)

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
options(scipen=10)
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
mod <- lm (log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
words.bottom.right.logxy(mod)

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7.5}
par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
     xlim=c(1,700000),ylim=c(1,700000),xlab="Total reproductive investment (mg)",ylab="Investment in accessory tissues (mg)")
abline(0,1)
abline(-0.30103,1)
abline(-1,1)
text(120,350,"all RE to accessory tissues",srt=45)
text(12000,720,"10% RE to accessory tissues",srt=45)
text(5,1.5,"50%",srt=45)

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm(asin(sqrt(seedset))~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
words.bottom.right.logy(mod)

mod <- lm(asin(sqrt(prop_propagule))~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
words.bottom.right.logy(mod)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
words.bottom.right.logxy(mod)
```

@@

###5. What influences the correlation between RA and plant size (or total reproductive investment)?
  ***Don't trust anything until I know RA and repro_inv are correct, because PHPH and PUTU have huge influence on patterns***
```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30,warning=FALSE}
par(mfrow=c(5,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))

@@

- just looking among plants >3 years old  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2)) 
tmp <- SummaryInd %>%
  filter(repro_inv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_prepollen_all)

@@

tmp2 <- SummaryInd %>%
  filter(repro_inv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_packaging_dispersal)

### 2015-08-19 Growth_figs.rmd
Rename *Inv variables

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "GrowthInv"
xvar <- "prop_maxH"

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "prop_maxH"

### 2015-08-19 Panalysis.rmd
Rename *Inv variables

```{r, echo=FALSE,results='hide', message=FALSE}
libReproInvry(remake)
create_bindings()

source("scripts/summary_datafReproInvmes.R")
source("scripts/functions.R")
```

@@

mod <- lm(log(ReproInv)~log((propagule_inv)),data=subset(SummaryInd,ReproInv>0&propagule_inv>0))
plot(propagule_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,ReproInv>0&prop_propagule>0))
plot(asin(sqrt(prop_propagule))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(ReproInv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,ReproInv>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~ReproInv,data=subset(SummaryInd,ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,ReproInv>0&prop_prepollen_aborted>0))
plot(asin(sqrt(prop_prepollen_aborted))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(ReproInv)~log((prepollen_success_inv)),data=subset(SummaryInd,ReproInv>0&prepollen_success_inv>0))
plot(prepollen_success_inv~ReproInv,data=subset(SummaryInd,ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,ReproInv>0&prop_prepollen_success>0))
plot(asin(sqrt(prop_prepollen_success))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(ReproInv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,ReproInv>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
abline(0,1)
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(ReproInv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,ReproInv>0&prop_packaging_dispersal>0))
plot(asin(sqrt(prop_packaging_dispersal))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(ReproInv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,ReproInv>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,ReproInv>0&prop_postpollen_aborted>0))
plot(asin(sqrt(prop_postpollen_aborted))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_all_count"
xvar <- "ReproInv"

@@

plot(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
text(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")

>>>>

```{r, echo=FALSE,results='hide', message=FALSE}
librepro_invry(remake)
create_bindings()

source("scripts/summary_datafrepro_invmes.R")
source("scripts/functions.R")
```

@@

mod <- lm(log(repro_inv)~log((propagule_inv)),data=subset(SummaryInd,repro_inv>0&propagule_inv>0))
plot(propagule_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,repro_inv>0&prop_propagule>0))
plot(asin(sqrt(prop_propagule))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(repro_inv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0))
plot(asin(sqrt(prop_prepollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(repro_inv)~log((prepollen_success_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_success_inv>0))
plot(prepollen_success_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0))
plot(asin(sqrt(prop_prepollen_success))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(repro_inv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
abline(0,1)
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(repro_inv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0))
plot(asin(sqrt(prop_packaging_dispersal))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(repro_inv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(repro_inv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0))
plot(asin(sqrt(prop_postpollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_all_count"
xvar <- "repro_inv"

@@

plot(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
text(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")

### 2015-08-19 RA_figs.rmd
Rename *Inv variables

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
words.top.left.logxy(mod)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")

plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")
```

@@

###RV curves by species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "ReproInv"
xvar <- "total_weight"

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "GrowthInv"
xvar <- "total_weight"

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "TotalInv"
xvar <- "total_weight"

>>>>

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
words.top.left.logxy(mod)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")

plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")
```

@@

###RV curves by species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_inv"
xvar <- "total_weight"

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight"

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_inv"
xvar <- "total_weight"

### 2015-08-19 errors_to_fix.rmd
Rename *Inv variables

###Problem.  
* There are two problems with the calculation of PEPU cones. I discovered this, because there were a few plants, especially PEPU_802, with huge ReproInv relative to repro_all_count  
* Looking at various data sources I discovered that the estimated FD (Final Development) parts weights for those cones were much too big, for PEPU_802 more than 10x too big  
* In addition, for PEPU_802 and PEPU_807 the aborted cones were actually collected and marked as "to use" in the flower parts data, but aren't being used
* I've looked at Konrad's scripts and can't immediately see what would be wrong

```{r}
plot(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
text(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")

@@

###Problem.
* The first plot below shows that there are individuals where absolute investment in accessory tissues is larger than total reproductive investmen* There are two different sources of reproductive investment, one which comes from the file "accessory" and is the sum of all the different accessory tissues and one which comes from the dataframe "investment". The "investment" variant is what is currently being used, but not sure which one should be being used
* They are quite different from each other
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
abline(0,1)
text(120,350,"all RE to accessory tissues",srt=45)

plot(investment$ReproInv~accessory$total_repro_inv,log="xy",pch=16,col=col.spp[as.factor(investment$species)])
```

>>>>

###Problem.  
* There are two problems with the calculation of PEPU cones. I discovered this, because there were a few plants, especially PEPU_802, with huge repro_inv relative to repro_all_count  
* Looking at various data sources I discovered that the estimated FD (Final Development) parts weights for those cones were much too big, for PEPU_802 more than 10x too big  
* In addition, for PEPU_802 and PEPU_807 the aborted cones were actually collected and marked as "to use" in the flower parts data, but aren't being used
* I've looked at Konrad's scripts and can't immediately see what would be wrong

```{r}
plot(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
text(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")

@@

###Problem.
* The first plot below shows that there are individuals where absolute investment in accessory tissues is larger than total reproductive investmen* There are two different sources of reproductive investment, one which comes from the file "accessory" and is the sum of all the different accessory tissues and one which comes from the dataframe "investment". The "investment" variant is what is currently being used, but not sure which one should be being used
* They are quite different from each other
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
abline(0,1)
text(120,350,"all RE to accessory tissues",srt=45)

plot(investment$repro_inv~accessory$total_repro_inv,log="xy",pch=16,col=col.spp[as.factor(investment$species)])
```
